% !TeX program = LuaLaTeX
\documentclass[letterpaper,12pt]{article}
\def \myrespresectionskip {-.25in}
\def \resumeitemizeskip{0in}
\def \jobskip{.075in}
\usepackage[inline]{enumitem}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{comment}
\usepackage[letterpaper,top=.25in,left=.75in,right=.75in,bottom=.25in]{geometry}
\usepackage[usenames,dvipsnames]{color}
  \definecolor{mygreylink}{RGB}{255,184,115}
  \definecolor{mygrey}{RGB}{14,43,3}
\definecolor{mymagent}{RGB}{72,4,23}
\definecolor{faded}{RGB}{66,82,121}
%\definecolor{mygrey}{RGB}{47,34,3}
  \definecolor{compliment}{RGB}{4,23,72}
\usepackage[pdftex]{hyperref}
  \hypersetup{
    colorlinks,
    citecolor=compliment,
    filecolor=compliment,
    linkcolor=compliment,
    urlcolor=compliment,
    pdftitle={Resume - Colin Versteeg},
    pdfauthor={Colin Versteeg},
pdfkeywords={Java, Computer Engineering, Engineering, Electrical Engineering, UMD, Maryland, Leadership, Python, Python, Microsoft, C\#, .Net Core, Git, Development, Software Development, REST, Big Data, R, Data Analytics}
  }
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{enumitem}
\newlist{resumeitemize}{itemize}{1}
\setlist[resumeitemize]{label=\textbullet,labelindent=-.25in,leftmargin=0pt,labelsep=.125in,itemsep=0em}
\newlist{skillsitemize}{itemize}{1}
\setlist[skillsitemize]{label={},labelindent=-.25in,leftmargin=0pt,labelsep=.125in,itemsep=0em}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\setmainfont{Minion Pro}
  \color{compliment}
\setsansfont{Myriad Pro}
\renewcommand{\arraystretch}{0.5}
\setlength{\tabcolsep}{0in}
\setlength\parindent{0pt}
\usepackage[sc,tiny]{titlesec}
%\titleformat{\section}{\sffamily\scshape\footnotesize}{\thesection}{1em}{}
\titleformat\section{\textcolor{mymagent}{\hrule}\sffamily\sc}{\thesection}{1em}{}

\newcommand{\myheader}{
\begin{center}
    \href{http://www.linkedin.com/pub/colin-versteeg/5b/26b/1b8}{{\huge\bf\sffamily Colin Versteeg}} \\
   \sffamily 1408 E. Union St. Apt 403 \textbullet \, Seattle, WA 98122 \\ 
\href{callto:3015185620}{\sffamily(301) 518-5620} \textbullet \, \href{mailto:cverstee@gmail.com}{\sffamily cverstee@gmail.com} 
\end{center}
}
\newcommand{\resheading}[5]{
\large{\textbf{#1}}\hfill{\rmfamily\normalsize\textcolor{faded}{#2}} \\
\normalsize{#3}\hfill{\textcolor{faded}{\normalsize#4}}\\
\normalsize{#5}
\normalsize
}
\pagestyle{empty}
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\title{Resume - Colin Versteeg}
\author{Colin Versteeg}

\begin{document}

\myheader
\vspace{-.3in}

\section*{Professional Experience}
\resheading{{Microsoft}}{Aug. 2016 \--}{{AI and Research}}{Redmond, WA}{\emph{Software Engineer}}
{ \footnotesize
\vspace{\resumeitemizeskip}
      \begin{resumeitemize}
	\item{Developed Operationalization software for Machine Learning in Microsoft Machine Learning Server and SQL Server}
	 \item{Designed and implemented support for Python in Microsoft Machine Learning Server Operationalization}
          \end{resumeitemize}
}
\resheading{{Booz Allen Hamilton}}{June 2015 \-- Aug. 2015}{\emph{Malware Intern}}{Annapolis Junction, MD}{}
{ \footnotesize
\vspace{-.2in}
      \begin{resumeitemize}
	\item{Developed web-based software prototype to automate portions of malware analysis using Apache Storm, Java and Python to support 20+ consultants serving government and commercial clients}
	\item{Developed for the full stack in a four intern team to complete the initial scope of the project and expand the scope by 25\%}
          \end{resumeitemize}
}
\vspace{\jobskip}
\resheading{{Food and Drug Administration}}{May 2014 \-- Aug. 2014; Jan. 2015}{{Center for Devices and Radiological Health}}{Silver Spring, MD}{\emph{Mathematics and Statistics Trainee}} 
   { \footnotesize
\vspace{\resumeitemizeskip}
      \begin{resumeitemize}
	 \item{Selected in a competitive application process to research non-linear metrics to assess image quality in {X-ray CT} for regulating machine learning advances in iterative reconstruction}
            \item{Developed a public-domain software package for easy performance of LROC and EFROC reader studies in Python with NumPy and \textsc{Matlab} to assist industry in evaluating performance of non-linear statistical models}
          \end{resumeitemize}
   }
\vspace{\jobskip}
\resheading{{Food and Drug Administration}}{May 2013 \-- Aug. 2013}{{Center for Devices and Radiological Health}}{Silver Spring, MD}{\emph{Volunteer Research Intern}}
   { \footnotesize
\vspace{\resumeitemizeskip}
   }
\vspace{\myrespresectionskip}
\section*{Education}
\resheading{{University of Maryland}}{May 2016}{Computer Engineering; GPA: 3.3}{College Park, MD}{}\footnotesize
 \begin{resumeitemize}
	\vspace{-.2in}
            \item{\href{http://www.scholars.umd.edu/programs/pl}{College Park Scholars: Public Leadership} --- Citation Recieved: October 2014}

          \end{resumeitemize}

\vspace{\myrespresectionskip}
\section*{Leadership Experience}
\resheading{{University of Maryland Men's Ultimate}}{Aug. 2014 \-- May. 2016}{\emph{Co-Captain, B Team}}{College Park, MD}{}
   { \footnotesize
\vspace{-.2in}
      \begin{resumeitemize}
	\item{Collaborated with two co-captains to lead team of 50+ players in 8 hours of practice a week and monthly competitions to an undefeated season and regional championship.}
	\item{Managed team budget of over \$5000 for tournament fees and apparel orders}
          \end{resumeitemize}
}
\vspace{\jobskip}
\resheading{{University of Maryland}}{Sep. 2014 \-- Dec. 2014}{{Department of Electrical and Computer Engineering}}{College Park, MD}{\emph{Undergraduate Teaching Fellow, Engineering Ethics}}
   { \footnotesize
\vspace{\resumeitemizeskip}
      \begin{resumeitemize}
	\item{Led discussion section of 12 students and graded student work to teach importance of engineering ethics and professionalism.}
          \end{resumeitemize}
}
\vspace{\myrespresectionskip}
\section*{Skills}
\begin{skillsitemize} 
\resitem{\textbf{Programming Languages}: Python, C$^\sharp$, Java, R, F$^\sharp$}
\resitem{\textbf{Platforms}: Windows, Linux, .NET Core, Apache Storm, Jupyter, Bash Scripting}
\end{skillsitemize}
\end{document}

